---
title       : Stock Quote Application
subtitle    : Developing Data Products Course Project
author      : CY Kan
job         : Coursera Signature Track Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Stock Quote Application

### Introduction

The Shiny application is a simple stock analysis application, providing the following features:

1. Support of any stock symbol available at Yahoo! Finance
2. Customizable date range
3. Inclusion of Simple Moving Average with configurable period parameter
4. Selection of candlestick or line chart types
5. Beautiful price chart of the stock

--- .class #id 

## Stock Quote Application

### How to use the app

| UI Inputs | Description
| --------- | -----------
| Symbol | The stock symbol of interest
| Date Range | The start and end dates of the price chart
| Chart Type | Either candle (default) or line can be chosen
| Simple Moving Average | Tick to superimpose Simple Moving Average on the price chart
| Period (Days) | Period of the Simple Moving Average, default 10 days
| Refresh Chart | Button to refresh the price chart         

--- .class #id

## Stock Quote Application

### How the price chart works

The charting features of this application is provided by quantmod, a quantitative financial modelling & trading framework for R. Its details can be found at <http://www.quantmod.com/>.

The stock quote data is retrieved by calling ```getSymbols()``` function with the stock symbol as the parameter.

```{r}
library(quantmod)
str(getSymbols)
```

--- .class #id

## Stock Quote Application

### How the price chart works

The price chart can then be created by calling ```chartSeries()``` function with appropriate chart settings.

```{r}
str(chartSeries)
```
